method

### 2021-10-06 06_Paper/ER-ED/method.Rmd
added questionnaires
added text

_Part one: ER task._ <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.4. Stimuli](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

_Part two: ER effort discounting._ <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with an addition to be useful for the current study.
We used an adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one.

[...]
For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies  with monetary values were presented.
The order of the comparisons was randomized.
Because there is no strategy that is objectively more difficult, all comparisons began with 
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

@@

## 2.4. Stimuli
```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

@@

Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
This survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

>>>>

_Part one: ER task._ <br>
Part one could be described as standard ER task that followed a block design (see Figure X), similar to paradigms previously used by our group [@Scheffel2021]. 
Participants were told to actively view neutral and negative pictures (see [2.4](##stimuli)) or to regulate all upcoming emotions by means of distraction, distancing and expressive suppression, respectively. 
Every participant first had the condition "active viewing-neutral" that served as a baseline condition.
During this block, 20 neutral pictures were presented.
Participants were asked to "actively view all pictures and permit all emotions that may arise."
In the second block, participants actively viewed negative pictures.
During the third, fourth, and fifth block, participants saw negative pictures and were asked to regulate their emotions using distraction, distancing, and suppression.
In order to achieve distraction, participants were asked to think of a geometric object or an everyday activity, like brushing their teeth.
During distancing, participants were asked to "take the position of a non-involved observer, thinking about the picture in a neutral way."
Participants were told not to re-interpret the situation or attaching a different meaning to the situation.
During suppression, participants were told to "suppress their emotional facial expression."
They should imagine being observed by a third person that should not be able to tell just by looking at the facial expression whether the person is looking at an emotional picture.
Participants were instructed not to suppress their thoughts or change their facial expression to the opposite [@Scheffel2021].
All participants received written instruction and completed a training session.
After the training session, participants were asked about their applied ER strategies to avoid misapplication.
The order of the three regulation blocks (distraction, distancing, and suppression) was randomized between participants.

_Part two: ER effort discounting._ <br>
In the second part, ER effort discounting took place.
The procedure of the discounting followed the COG-ED paradigm by Westbrook et al. [-@Westbrook2013] with major change (see [1.1](##adapting an effort discounting paradigm)).
We used the following adaption that allowed the computation of SVs for different strategies without presuming that all individuals would inherently evaluate the same strategy as the easiest one: For each possible pairing (distraction vs. distancing, distraction vs. suppression, and distancing vs. suppression), two strategies with monetary values were presented.
The order of the comparisons was randomized.
Because there is no strategy that is objectively more difficult, all comparisons began with 
Participants were instructed to decide as realistically as possible, imaging the displayed money would really be up for election.

@@

## 2.4 Stimuli
```{r stimvalues, echo = FALSE}
# import excel list with neutral and negative pictures
# lists contain arousal and valence values of each picture
stim_negative = readxl::read_xlsx(file.path(here("01_Paradigms","ER-ED","ER_ED","Stimuli","negative.xlsx")), range = cell_cols("A:D"))

@@

Two days after the T2 ER session, participants receive an email containing the link to the online survey. 
This survey contained a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] was used. 
Dispositional use of ER was assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we used the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control were assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017] was used.
To assess need for cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] was used.
To assess self-control, sum scores of the following questionnaires were used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
Attentional control was assessed using the Attentional Control Scale (ACS) [@Derryberry2002].
